---
title: "gtsummary in quarto"
format:
  html:
    theme: sketchy
execute:
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")))
         sex_cat = factor(sex, labels = c("Male", "Female"))
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic"))
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor"))
         glasses_cat = factor(glasses, labels = c("No", "Yes"))
```

# Customization of `tbl_summary()`

```{r}

tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))

```

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```

# About NLSY

The NLS, sponsored by the U.S. Bureau of Labor Statistics, are nationally representative surveys that follow the same sample of individuals from specific birth cohorts over time. This study included `r nrow(nlsy)` participants. @tbl-one displays demographics of the study cohort.


```{r}
#| label: tbl-one
#| tbl-cap: "NLSY demographics table stratified by sex"

table_one<-tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
inline_text(table_one, variable=region_cat, column=male)
```

```{r}
mean_sleep_wknd<- mean(nlsy$sleep_wknd, na.rm = TRUE)

```
The average amount of sleep participants received on weekends was `r round(mean_sleep_wknd,2)` hours. `r median(nlsy$sleep_wknd, na.rm = TRUE)` is the median hours of weekend sleep for participants.

```{r}
#| error: true
#| label: tbl-two
#| tbl-cap: "This is a great table"
knitr::kable(mtcars)

```

